Fast Neural Machine Translation Implementation

### 2018-05-18 wnmt.2018/wnmt.tex
bah

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{pie-time.png}} 
\end{tabular}
\caption{Proportion of time spent during translation}
\label{fig:pie-time}
\end{figure}

@@

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{decode-step.png}} 
\end{tabular}
\caption{Time taken for each decoding step for a batch of 1280 sentences}
\label{fig:decode-step}
\end{figure}

@@

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{batch-size.png}} 
\end{tabular}
\caption{Speed v. batch size}
\label{fig:batch-size}
\end{figure}

@@

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{fused.png}} 
\end{tabular}
\caption{Using fused operation}
\label{fig:fused}
\end{figure}

>>>>

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.35]{pie-time.png}} 
\end{tabular}
\caption{Proportion of time spent during translation}
\label{fig:pie-time}
\end{figure}

@@

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.35]{decode-step.png}} 
\end{tabular}
\caption{Time taken for each decoding step for a batch of 1280 sentences}
\label{fig:decode-step}
\end{figure}

@@

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.35]{batch-size.png}} 
\end{tabular}
\caption{Speed v. batch size}
\label{fig:batch-size}
\end{figure}

@@

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.35]{fused.png}} 
\end{tabular}
\caption{Using fused operation}
\label{fig:fused}
\end{figure}
